Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-15 prop_iop.tex
prop_iop.tex \section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}} Updating...

\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
  Given a Hilbert space $\Hilb$ with quantum events
  (projections)~$\events$, and a collection of
  intervals~$\mathscr{I}$, a \emph{quantum
    $\mathscr{I}$-interval-valued probability measure} is a
  function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ such that:
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any projection $P$,
  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
\item For a set of mutually orthogonal projections
  $\left\{ P_{i}\right\} _{i=1}^{N}$, we have
  $\bar{\mu}\left(\sum_{i=1}^{N}
    P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
\end{itemize}
\end{definition}

@@

\begin{thm}Given a Hilbert space~$\Hilb$ of dimension~$3$, every
quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is convex.\end{thm}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{}%
\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}

>>>>

\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
Given a Hilbert space $\Hilb$ with quantum events (projections)~$\events$,
and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
probability measure} is a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that: 
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any projection $P$, 
\begin{equation}
\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
\end{equation}
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
\end{definition}

@@

\begin{thm}\label{thm:convex-3}Given a Hilbert space~$\Hilb$ of
dimension~$3$, every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is convex.\end{thm}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}}

\begin{example}[Three-dimensional quantum three-value interval-valued
probability measure]\label{ex:three-dimensional-three-value-1} Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
and $\ket{\ps}=\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$.
Let 
\begin{equation}\eqalign{ 
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\textrm{ ,}\\ 
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,}\\ 
\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
}\end{equation}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check 
\[
\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
\]
for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)$.

Next, since the dimension of the Hilbert space is three, $\bar{\mu}$
is convex by theorem~\ref{thm:convex-3}.

Finally, we will prove that $\bar{\mu}$ cannot correspond to any
quantum probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
We must have $\mu(\proj{0})=\mu(\proj{\ps})=0$. By Gleason's theorem,
there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. If $\ip{\phi}{0}=\ip{\phi}{\ps}=0$,
we must have $\ket{\phi}=\ket{2}$, i.e., $\rho=\proj{2}$. However,
$\mu(\proj{2})=\ip{2}{2}\ip{2}{2}=1\notin\unknown=\bar{\mu}\left(\proj{2}\right)$.
Therefore, $\bar{\mu}$ has an empty core.\qed\end{example}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\newpage{}%
\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}
